### 2024-05-26 mythbusters.qmd
20240526 - contract year

>>>>

## Do Players Score More Points in their Contract Year? {#sec-contractYear}

```{r}
nfl_playerContracts_subset %>% 
  filter(player == "Aaron Rodgers") %>% 
  select(player:years, contractYear, next_contract_start, played_in_contract_year)

nfl_playerContracts_subset %>% 
  filter(player %in% c("Jared Allen", "Aaron Rodgers")) %>% 
  select(player:years, contractYear, next_contract_start, played_in_contract_year)

# Subset to remove players without a year signed
nfl_playerContracts_subset <- nfl_playerContracts %>% 
  filter(!is.na(year_signed) & year_signed != 0)

# Determine the contract year for a given contract
nfl_playerContracts_subset$contractYear <- nfl_playerContracts_subset$year_signed + nfl_playerContracts_subset$years - 1

# Arrange contracts by player and year_signed
nfl_playerContracts_subset <- nfl_playerContracts_subset %>%
  group_by(player, position) %>% 
  arrange(player, position, -year_signed) %>% 
  ungroup()

# Determine if the player played in the original contract year
nfl_playerContracts_subset <- nfl_playerContracts_subset %>%
  group_by(player, position) %>%
  mutate(
    next_contract_start = lag(year_signed)) %>%
  ungroup() %>%
  mutate(
    played_in_contract_year = ifelse(
      is.na(next_contract_start) | contractYear < next_contract_start,
      TRUE,
      FALSE))

# Merge with seasonal fantasy points data
```
